pattern_explore

### 2022-06-06 paper_comparison/explore/check_patterns.Rmd
check sigma for poly model

>>>>

```{r fig.height=34, fig.width=45, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-0.1, 0.1), sigma = 0.25)
ori_dat <- mod$gen(1000, computed = list(e = rep(0, 1000)))
i <- 0
plot_list <- list()

for (a in c(-1.5, -1, -0.1, -0.01, -0.001, -0.0001, 0, 0.0001, 0.001, 0.01, 0.1, 1, 1.5)) {
  for (b in c(-1.5, -1, -0.1, -0.01, -0.001, -0.0001, 0, 0.0001, 0.001, 0.01, 0.1, 1, 1.5)) {
    i <- i + 1
    mod$set_prm("a", a) %>%
      {.$set_prm("b", b)} %>%
      {.$gen(1000, computed = select(ori_dat, x, e))} %>%
      {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE)} +
      ggtitle(glue::glue("a:{a}, b:{b}, a/|b|:{a/abs(b)}")) -> plot_list[[i]]
  }
}

```{r}
result <- tibble()

for (a in seq(-1.5,1.5,0.25)) {
  x <- rand_uniform(-1, 1)
  e <- rand_normal(sigma = 0.25)
  y <- closed_form(~x+a*x^2 + e)

  dat <- y$gen(10000, rhs_val = TRUE, computed = list(e = 0)) %>%
    y$as_dataframe("y")

  mod <- lm(y ~ x, data = dat)

  result <- bind_rows(result, tibble(.pred = predict(mod) - mean(predict(mod)),
                                     .resid = resid(mod),
                                     a = a))
}

result %>%
  ggplot() +
    geom_line(aes(.pred, .resid, col = factor(a))) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          # axis.text.x = element_blank(),
          # axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  theme_bw() +
  ggtitle(quote("centered fitted values vs. residuals"~of~y~"="~x), subtitle = quote(y~"="~x+ax^2+e)) +
  xlab("fitted values") +
  ylab("residuals")

result %>%
  ggplot() +
    geom_line(aes(.pred, .resid)) +
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.line = element_blank(),
          axis.ticks = element_blank(),
          # axis.text.x = element_blank(),
          # axis.text.y = element_blank(),
          axis.title.x = element_blank(),
          axis.title.y = element_blank()) +
  facet_wrap(~a, scales = "free")
```
